\documentclass[a4paper]{article}
%\usepackage{simplemargins}

%\usepackage[square]{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

\begin{document}
\pagenumbering{gobble}

\Large
 \begin{center}
Modal definability in precompact polyhedra\\ 

\hspace{10pt}

% Author names and affiliations
\large
Francesco Tognetti$^1$ \\

\hspace{10pt}

\small  
$^1$) University of Luxembourg\\
francesco.tognetti@uni.lu

\end{center}

\hspace{10pt}

\normalsize

\noindent The aim of the paper is to prove an equivalent of Goldblatt-Thomason's theorem for classes of precompact polyhedra, i.e. subsets of the affine space whose closure is a compact polyhedron.

	We adapt from the semantics from \cite{DBLP} on compact polyhedra, where the closure operator $\lozenge$ acts as a closure on subpolyhedra, to draw a closer connection between polyhedra and what we call 'simplicial precomplexes', some combinatorial objects, that generalize simplicial complexes.
	
	This allows us to swiftly translate conditions between polyhedra -as geometric objects,  precomplexes - as combinatorial objects, and posets, giving us a result similar to\cite{Stop}
	\begin{enumerate}
		\item  Any class of polyhedra is equivalent to the realization of a class of simplicial precomplexes closed under subdivision.
		\item A class of (finite) simplicial precomplexes is modally definable if and only if it's closed under disjoint unions, open simplicial images, and open subcomplexes
		\item A class of polyhedra is modally definable if and only if it's closed under disjoint unions, open PL-maps and open subpolyhedra.
	\end{enumerate}

\noindent As simplicial complexes (and their realization) carry topological meaning, we can obtain a negative result on homological properties:
\begin{enumerate}
	\addtocounter{enumi}{3}
	\item The homology chains of a modally definable class of simplicial complexes must be closed under direct sums and images
\end{enumerate}

Thus excluding the definability of any class of the kind ``polyhedra of a certain genus''
	
\begin{thebibliography}{9}
\bibitem{DBLP} Nick Bezhanishvili et al. “Geometric Model Checking of Continuous Space”. In: CoRR
abs/2105.06194 (2021). arXiv: 2105.06194. url: https://arxiv.org/abs/2105.06194.

\bibitem{Stop}
\end{thebibliography}
\end{document}