\section{Definability of compact polyhedra}

\cite{Blackburn_Rijke_Venema_2001} in chapter 3 gives us a definability result for classes of finite transitive frames

\begin{theorem}

A class of finite transitive frame is modally definable if and only if it's closed under finite disjoint union,
bounded morphic images and generated subframes.
\end{theorem}

Suppose we have a class of simplicial complexes, it's modally definable if and only if the corresponding class of posets is.

We want to translate these conditions in terms of simplicial complexes and then realize them in terms of polyhedra.

The picture we want to have in mind when building classes is the following: 

\[\begin{tikzcd}[ampersand replacement=\&]
	\& C \\
	{[C]} \& \Scplx \& {|C|} \\
	\Pos \&\& \Pol
	\arrow[from=1-2, to=2-1]
	\arrow[hook, from=1-2, to=2-2]
	\arrow[from=1-2, to=2-3]
	\arrow[hook, from=2-1, to=3-1]
	\arrow["{[-]}", from=2-2, to=3-1]
	\arrow["{|-|}", from=2-2, to=3-3]
	\arrow[hook, from=2-3, to=3-3]
	\arrow["\Nn", shift left=3, from=3-1, to=2-2]
\end{tikzcd}\]

\subsection{Disjoint union}

Let us start with disjoint unions: these are the easiest construction since they are the same in all three settings

\begin{proposition}
    For a pair of simplicial complexes $\Sigma, \Sigma'$, 
    $[\Sigma\sqcup\Sigma']=[\Sigma]\sqcup[\Sigma']$
\end{proposition}
\begin{proof}
    Let $\sigma$ be a simplex of $[\Sigma\sqcup\Sigma']$, then -as the union is disjoint- it must be a simplex of either $[\Sigma]$ or $[\Sigma']$, and vice versa.
\end{proof}

Similarly
\begin{proposition}
    For a pair of simplicial complexes $\Sigma,\Sigma'$, $|\Sigma\sqcup \Sigma'|=|\Sigma|\sqcup|\Sigma'|$
\end{proposition}
\begin{proof}
    There are direct ways to show it but we appeal to abstract nonsense and say that the geometric realization is the coend 
    \[\int^{n\in \N}\Delta^n\cdot \Sigma_n\] 
    thus the constructions commutes with colimits.

    This is not as clear, but theoretically better than a direct proof in $\R^n$ 
    since it eventually will allow us to work with arbitrarily-sized polyhedra too.
\end{proof}

This means that
\begin{lemma}
    A class of simplicial complex $C$ is closed under disjoint union if and only if its corresponding class of posets $[C]$ is closed under disjoint union
    if and only if its corresponding class of polyhedra $|C|$ is closed under disjoint union.
\end{lemma}

\subsection{generated subframes}

Now suppose we have a simplicial complex $\Sigma$: What corresponds to generated subframes of $[\Sigma]$?

Recall that
\begin{definition}[Generated subframe]

    A \textbf{Generated subframe} of a kripke frame $(W,R)$, is a subset $W'\subseteq W$ closed upwards under $R$.
\end{definition}

Recall that the posets we are considering are the 'coface' posets, i.e. the posets whose 
elements are the faces of $\Sigma$ and whose relation is the opposite of the inclusion.

This means that a generated subframe is $\uparrow-$closed under $\supseteq$, thus $\downarrow-$closed under $\subseteq$.

in other words 
\begin{lemma}\hfill

    Let $C$ be a class of simplicial complexes, then $[C]$ is closed under generated subframes if and only if $C$ is closed under
    subcomplexes. 
\end{lemma}
\begin{proof}\hfill 
    Let $\Sigma$ be a simplicial complex and $\Sigma'$ a subcomplex. 
    As $\Sigma'$ is a complex as well, then it's downward-closed.
    
    Conversely, if $S'\leq[\Sigma]$ is a downward-closed subposet, 
    then by definition it's closed under taking subsets, thus it's a simplicial complex.
\end{proof}

\begin{lemma}
    Let $C$ be a class of simplicial complexes, then $|C|$ is closed under subpolyhedra if and only if 
    $C$ is closed under subcomplexes and triangulations.
\end{lemma}
\begin{proof}
    if $\Sigma'\leq \Sigma$ is a subcomplex then $|\Sigma'|\subseteq |\Sigma|$ is a closed subpolyhedron.

    Conversely, if $S\subseteq |\Sigma|$ is a closed subpolyhedron, then there exists a triangulation of $|\Sigma|$
    that triangulates $S$, meaning that there exist two simplicial complexes $\Sigma',\Sigma''$ such that $|\Sigma'|=S,\ |\Sigma''|=|\Sigma|$
\end{proof}

\subsection{bounded morphic images}

Lastly we need to interpret bounded morphism in our triad. Recall 
\begin{definition}\hfill 

    Let $(W,R)$ and $(W',R')$ be kripke frames and $f:W\to W'$ a function.

    $f$ is a \textbf{bounded morphism} if and only if 
    \begin{itemize}
        \item $wRv$ implies $f(w)R'f(v)$
        \item $f(w)R' v'$ implies that there exists $v$ such that $wRv$ and $f(v)=v'$.
    \end{itemize}
\end{definition}

Interpreting this as the coface relation this means 
\begin{itemize}
    \item $\sigma\subseteq \tau$ implies $f(\sigma)\subseteq f(\tau)$
    \item $\sigma'\subseteq f(\tau)$ implies that there exists $\sigma\subseteq \tau$ such that $f(\sigma)=\sigma'$
\end{itemize}

Let's define a class of simplicial maps:
\begin{definition}[Bisimplicial map]\hfill 
    
    Let $(V,\Sigma),(V',\Sigma')$ be simplicial complexes. $f:V\to V'$ is called a \textbf{bisimplicial map} if 
    \[\forall s\in \Pp(V), f(s)\in \Sigma' \iff s\in \Sigma\]
\end{definition}

\begin{lemma}\hfill 
    
    A map of simplicial complexes $f:\Sigma\to\Sigma'$ induces a bounded morphism $[\Sigma]\to[\Sigma']$ if and only if it's bisimplicial.
\end{lemma}
\begin{proof}
    Suppose $f$ is a bisimplicial map, then suppose 
    $\sigma\subseteq \tau$, then $f(\sigma)$ and $f(\tau)$ are simplices and $f(\sigma)\subseteq f(\tau)$ as it's an image map.

    Now suppose $\sigma'=f(\tau)$. suppose $\tau=v_1,...,v_n$, thus $f(\tau)=f(v_1),...,f(v_n)$. up to reordering, $\sigma'=f(v_1),...,f(v_k)$.
    As $f$ is bisimplicial, $f(v_1),...,f(v_k)=f(v_1,...,v_k)$ is a simplex, thus $\sigma:=v_1,...,v_k$ is a simplex and - by structure- a subsimplex of $v_1,...,v_n$. 
    
    Now conversely, suppose that $f$ is a bounded morphism $[\Sigma]\to[\Sigma']$, the (co)induced $f:\Sigma\to\Sigma'$

    First we need to check that image of a vertex is a vertex. This is because vertices are simplices, and minimal ones at that:
    suppose we have a vertex $v$ such that $f(v)=\sigma'$. then if $\sigma'$ is not a vertex, there exists $w'\subsetneq \sigma'=f(v)$.

    This means that there must exist $w\subseteq v$ such that $f(w)=w'$, but such $w$ does not exist as $v$ is minimal. $\to\gets$.

    Image of a simplex is a simplex (by definition), and suppose 
    
    $f(v_1,...,v_n)$ is a simplex of $\Sigma'$ but $v_1,...,v_n$ is not a simplex of $\Sigma$. but $f(v_1,...,v_n)=f(v_1,...,v_n)$ (thus in particular $\subseteq$)
    But then there exist a simplex $v_1,...,v_k\subseteq v_1,...,v_n$ such that $f(v_1,...,v_k)=f(v_1,...,v_n)$. But then for a question of cardinality it must be the case that
    $v_1,...,v_k=v_1,...,v_n$, thus $v_1,...,v_n$ is a simplex of $\Sigma$.
\end{proof}

Now to interpret bisimplicial maps as maps of polyhedra: 

Suppose we have the map $|f|:|\Sigma|\to|\Sigma'|$ that is the realization of a map $f:\Sigma\to\Sigma'$. 

If $f$ is bisimplicial, then this results in the conditions
\begin{itemize}
    \item if $\Hull(v_1,...,v_k)\subseteq |\Sigma|$, then $f(\Hull(v_1,...,v_k))=\Hull(f(v_1),...,f(v_k))\subseteq |\Sigma'|$, and 
    \item if $\Hull(f(v_1),...,f(v_k))\subseteq |\Sigma'|$, then $\Hull(v_1,...,v_k)\subseteq |\Sigma|$
\end{itemize} 

This is equivalent to it being a retraction onto the image:
\begin{theorem}
    Suppose $f$ if a map $\Sigma\to\Sigma'$, then it's a bisimplicial map if and only if $f:\Sigma\to\im(f)$ is a retraction.
\end{theorem}
\begin{proof}\hfill 
    Suppose that $f$ is bisimplicial.

    First, note that $f$ is surjective onto the vertices of $\im(f)$. 
    Moreover if $\sigma'=v_1',...,v_k'$ is a simplex in $\im(f)$, then there exist $v_1,...,v_k$ such that $f(v_i)=v_i'$ and $v_1,...,v_k$ is a simplex in $\Sigma$.

    This means that $f:\Sigma\to\im f$ is epimorphic at the level of simplices as well. 
    Now let $g:\im(f)\to \Sigma$ be defined as $g(v_i')=v_i$ for some $v_i$ such that $f(v_i)=v_i'$

    This is a well-defined map, sending vertices to vertices, and $f(g(v_1',...,v_n'))=f(v_1,...,v_n)=v1',...,v_n'$ thus $fg=1_{\im(f)}$

    Conversely, suppose that $f$ is a section, i.e. there exists a $g:\im(f)\to \Sigma$ such that $fg=1_{\im(f)}$
    Then suppose $f(v_1),...,f(v_n)=v_1',...,v_n'$ is a simplex. then $g(v_1'),...,g(v_n')=v_1,...,v_n$ is a simplex since $g$ is simplicial.
\end{proof}

\begin{corollary}
    Let $C$ be a class of simplicial complexes, then $|C|$ is closed under retracts if and only if $C$ is closed under bisimplicial images and triangulations. 
\end{corollary}
\begin{proof}
    $\PL-$retracts of $|\Sigma|$ are retracts of a triangulation of $\Sigma$ which are bisimplicial images by the lemma above.
\end{proof}
\subsection{Compact Goldblatt-Thomason for polyhedra}

Recall that the frames we defined are models for a modal logic (described extensively in \cite{DBLP}):

Essentially propositions are interpreted in unions of open subpolyhedra, $[\lozenge\phi]$ is the least closed subpolyhedron containing $[\phi]$.

We connect those as simplicial models by associating every simplex of a complex $\Sigma$ to its relative interior in $|\Sigma|$, thus obtaining a neighborhood-description:

\begin{corollary}
    If $\Sigma$ is a simplicial complex, for each point $x\in |\Sigma|$ there exists a unique face $\sigma\in\Sigma$ such that $x\in \sigma$, and 
    such $\Sigma$ can be interpreted as a poset through the face (or coface) relation.
\end{corollary}

Here we can finally express the main result of this paper:
\begin{theorem}[Compact GTT for Polyhedra]\hfill 

A class of compact polyhedra is modally definable if and only if it's closed under disjoint unions, closed subpolyhedra and retractions. 
\end{theorem}
\begin{proof}

    There's a direct correspondence between classes of polyhedra and class of simplicial complexes closed under triangulations: Indeed we showed that 
    two simplicial complexes are $\PL-$homeomorphic if and only if they have a common triangulation, thus the triangulation-equivalence forms the kernel 
    of the realization functor.

    As the constructions we built are stable under triangulation (indeed, up to triangulation equivalence, $\N$ and $[-]$ are inverses!),
    we have an equivalence between modally definable classes of polyhedra and of simplicial complexes 
    modulo triangulation.
\end{proof}