\section{GTKP}
\subsection{Face up-reductions}
To any poset we can assign to it a topology that is compatible with topological semantics.

\begin{definition}{Alexandrov topology}\hfill 

Let $(P,\leq)$ be a poset. We call the \textbf{Alexandrov} topology on $P$ 
$\tau\subseteq \Pp P$ where $U\in\tau$ if and only if $U$ is upward-closed.
\end{definition}

We will use it to define a weaker version of the up-reduction between polyhedra.
\begin{definition}{Face up-reduction}
    Let $P,Q$ be (compact) polyhedra and $K$ a triangulation of $Q$.

    A \textbf{face up-reduction} $P\fupred Q$ is a partial map $f:P\upred [K]$ 
    such that 
    \begin{enumerate}[(i)]
        \item The preimage of every open of $[K]$ (in the Alexandrov topology) is an open subpolyhedron of $P$
        \item It is \textbf{open}
        \item It is \textbf{Surjective}.
    \end{enumerate}
\end{definition}

Note that
\begin{proposition}\hfill 

    $Q\upred[K]$ for any triangulation $K$.

    In particular $Q\fupred Q$.
\end{proposition}
\begin{proof}\hfill 

    Let $K$ be a triangulation of $Q$ and recall that for every point 
    $q\in Q$ there exists a unique face $\sigma_q$ of $K$ such that $q\in\sigma_q$, thus 
    the map is trivially surjective.

    Let $f$ be the map $q\mapsto \sigma_q$.

    This means that the face of the polyhedron $|\sigma|=f^{\gets}(\sigma)$.

    If $U$ is an upward-closed set of $[K]$, then $[K]\setminus U$ is downward-closed,
    thus is a compact polyhedron.
    This means that $f^\gets([K]\setminus U)=Q\setminus f^{\gets}(U)$ is compact, thus closed,
    therefore $f^\gets(U)$ is open and is the union of faces, thus an open subpolyhedron.

    This same argument shows that the map is open:
    If $P\subseteq Q$ is an open subpolyhedron, then $Q\setminus P$ is a compact polyhedron, thus 
    $[K]\setminus f(P)$ is downward-closed, thus $f(P)$ is upward-closed, i.e. open.
\end{proof}
\begin{corollary}\hfill 

    If there exists an up-reduction, 
    i.e. an open partial simplicial map $P\upred Q$
    whose domain is an open subpolyhedron of $P$ 
    then $P\fupred Q$
\end{corollary}


We may also make explicit the following fact:

\begin{lemma}{}\hfill 

    Let $f:P\fupred Q$ be a face up-reduction, $U\subseteq^o P$ is the domain of $f$ and 
    $L$ is the triangulation of $Q$ such that $f:U\upred [L]$.
    
    Then there exists a triangulation $K$ of $P$ such that
    \begin{itemize}
        \item $U$ is the union of relative interiors of faces of $K$, i.e. $U=\bigcup_{\sigma\in K_U}\RelInt\sigma$.
        \item $\tilde{f}:[K]\upred[L]$ defined as $\tilde{f}(\sigma_p)=f(p)$ is an up-reduction of posets.
    \end{itemize}
\end{lemma}
\begin{proof}\hfill 

    Note that $[L]$ is a \textbf{finite} poset and that 
    $\set{f^\gets(l):l\in L}$ is a collection of possibly open polyhedra in $P$.
    By the common triangulation lemma, we may extract a common triangulation $K$
    of all of them.

    Now, recall that for each point $p\in P$ there exists a unique face $\sigma_p$
    such that $p\in\RelInt(\sigma_p)$.
    This allows us to define $\tilde{f}$ as above. Uniqueness gives us that $\tilde{f}$ is 
    well-defined, and $f(\uparrow\sigma_p)=\uparrow f(p)$ by openness of $f$.
\end{proof}
\begin{lemma}[Up-reductions refute formulas]

    Let $P$ be a polyhedron, $S$ a poset, $P\upred S$ an up-reduction.

    If $S\not{\models} \varphi$ then $P\not\models\varphi$ as well.
\end{lemma}
\begin{proof}
    The proof goes essentially as the topological case in \cite{Gabelaia2001ModalDI}
\end{proof}

\subsection{Goldblatt-Thomason for Compact Polyhedra}
\begin{theorem}{GTKP}\hfill 

A class of compact polyhedra $\C$ is modally definable if and only if 
it's closed under finite disjoint unions and face up-reductions, i.e. 
\begin{enumerate}[(I)]
	\item if $P,Q\in \C$, then $P\sqcup Q\in \C$
	\item if $P\in C$ and $P\fupred X$, then $X\in \C$.
\end{enumerate}
\end{theorem}
\begin{proof}[Proof ($\implies$)]\hfill 

Let $\C$ be a modally definable class, i.e. $\C=\set{P\in \Pol:P\models F}$ for some set of formulas $F$.

Closure under disjoint union is trivial, if $P,Q\in \C$, then $P\sqcup Q\models F$.

If $P\in \C$ and $P\fupred X$, then suppose $X\notin \C$.
By definition this means that there exists a formula $\varphi\in F$ such that $X\not{\models}\varphi$. 

Spelling out the validity condition,
there exists an evaluation $\nu:\Ll\to \Pp X$ and a point $x\in X$ such that $X,x\not{\models}\varphi$. 

By the simultaneous triangulation lemma, we may select a triangulation 
$S$ of $X$ such that $\nu(\varphi)$ is triangulated by $S$.

Now call $K=(V,\Sigma)$ the triangulation of $X$ realizing the face up-reduction $P\fupred X$.
	
By the 'nerves are dense' lemma,
we know that there exists a barycentric subdivision $K^{(n)}$ of $K$ subdividing $S$. 
	
We also know that we can extend any up-p-morphism $P\upred \Sigma$ to an up-p-morphism
$P\upred \Sigma^{(k)}$ for any $k\in \mathbb{N}$.
	
This means that we have an up-p-morphism 
$P\upred \Sigma^{(k)}\upred S$, therefore 
$P\not{\models}\varphi$, leading to a contradiction.
\end{proof}
\begin{proof}[Proof ($\impliedby$)]\hfill 

Let $\C$ be a class of polyhedra closed under (I) and (II),
call $L:=\Log(\C)$ and call $\C'=\Pol(L)$.

Clearly $\C\subseteq \C'$.
Let $X\in \C'$, we want to show that $X\in \C$.

We know that $X\models L$, and let $K=(V,\Sigma)\in \Tr(X)$. 

Call $v_i$ the vertices of $\Sigma$. We know that
 \[\bigsqcup_i (\uparrow v_i)\twoheadrightarrow \Sigma\]
is a p-morphism.

Consider $\chi_i:=\chi(\uparrow v_i)$ the Jankov-Fine formula for the (rooted) subposet. 

As $(\uparrow v_i)\not\models \chi_i$, we know that $\Sigma\not\models\chi_i$, 
as all $(\uparrow v_i)$ are generated subframes of $\Sigma$.

In particular $X\upred\Sigma$, thus $X\not\models\chi_i$, for all $i$.

This means that none of the $\chi_i$ are elements of $L$. 

This means that for each $\chi_i$ there exists some $P_i\in \C$ 
such that $P_i\not\models \chi_i$, thus $P_i\upred(\uparrow v_i)$.

This means that $P:=\bigsqcup_i P_i$ admits an up-p-morphism to $\bigsqcup_i(\uparrow v_i)$,
and we can take the composition with $\bigsqcup_i(\uparrow v_i)\twoheadrightarrow \Sigma$ 
to find an up-reduction $P\upred \Sigma$, thus a face up-reduction $P\fupred X$.

By (I) we know $P\in \C$, and by (II) $X\in \C$.
\end{proof}

\begin{corollary}
    
    A class of polyhedra closed under finite disjoint unions and simplicial up-reductions is 
    modally definable, where a simplicial up-reduction is an open simplicial partial map $f:P\upred Q$
    whose domain is an open subpolyhedron of $P$.
\end{corollary}
\begin{proof}
    Follows from Corollary 3.1.4:
    If $f:P\upred Q$ is a simplicial up-reduction, then there exists a face up-reduction $P\fupred Q$
    by composing with the face p-morphism onto any face poset.
\end{proof}

The theorem above is strengthened by the following lemma
\begin{lemma}[Any Triangulation]\hfill 

Let $P\upred \Sigma$ for a triangulation $L=(V,\Sigma)$ of $Q$, and let $L'=(V',\Sigma')$ be 
a different triangulation of $Q$. 
Then there exists an up-reduction $P\upred \Sigma'$.
\end{lemma}
\begin{proof}
Let $f:P\upred\Sigma$ be an up-reduction with domain $U\subseteq P$.

Then we can extend $f$ to $f^{(1)}:P\upred\Sigma^{(1)}$ in the following way:

Take the triangulation $K$ of $P$ realizing $f$ as a simplicial map $\tilde{f}$ (as per lemma 3.1.5)

Then utilize the subdivision lemma (lemma 1.3.4) to extract an up-reduction $K'\upred L^{(1)}$.

Now, utilizing lemma (1.3.3) we may repeat this $n$ times, such that $L^{(n)}$ is a subdivision of $L'$.

This means that we have a map $h: K^{\prime \cdots\prime }\upred L^{(n)}\twoheadrightarrow L'$

As $K^{\prime \cdots\prime }$ is a triangulation of $P$ we can extract an up-reduction $g:P\upred L'$ by 
setting it as locally constant on the relative interior of the faces of $P$.
\end{proof}

In other words, if a face up-reduction exists to a triangulation then one exists to any triangulation, 
even with the same domain.